Stack Safety as a Security Property

### 2020-07-10 main.tex
Clearer definition of return integrity

\definition%{Return Integrity}
A system enjoys {\em return integrity} if all of its returns match prior calls
and return to the appropriate location. For any initial state \((\mach_0\, \pol_0)\), let
\(\MPT\) be the induced trace of \(\mpstate{\mach_0}{\pol_0}\). Then two
conditions must hold.
\emph{(i)} \(\MPT\) must not have an unmatched return, i.e., \(\Unmatched ~ \MPT ~ \MPT_{\mathit{tail}}\)
must not hold for any \(\MPT_{\mathit{tail}}\). \emph{(ii)} For any state pair \((\mach_c, \pol_c)\)
corresponding to a call \(\MPT\), if
\(\mpstatename = \mpostate{\mach_r}{\_}{\_}\)
is the first unmatched return such that
\( \Unmatched ~ \MPT ~ \MPT_{\mathit{tail}}\) and \(\head{(\MPT_{\mathit{tail}})} = \mpstatename\),
then $\mach_r$ must correspond to a return state for $\mach_c$, i.e.,
\(\ret{\mach_c}\ \mach_r\) holds.\apt{This sentence still doesn't make sense to me.}

>>>>

\definition%{Return Integrity}
A system enjoys {\em return integrity} if all of its returns match prior calls
and return to the appropriate location.
For any initial state and its induced trace \((\mach_0\, \pol_0) \hookrightarrow \MPT\), two
conditions must hold.
\emph{(i)} \(\MPT\) must not have an unmatched return, i.e., \(\Unmatched ~ \MPT ~ \MPT_{\mathit{tail}}\)
must not hold for any \(\MPT_{\mathit{tail}}\).
%
\emph{(ii)} For any state pair \((\mach_c, \pol_c)\)
corresponding to a call in \(\MPT\), if
\(\MPT_{\mathit{call}}\) is the suffix of the trace starting at the call,
\(\mpstatename = \mpostate{\mach_r}{\_}{\_}\)
is the first unmatched return such that
\( \Unmatched ~ \MPT_{\mathit{call}} ~ \MPT_{\mathit{tail}}\) and \(\head{(\MPT_{\mathit{tail}})} = \mpstatename\),
then $\mach_r$ must correspond to a return state for $\mach_c$, i.e.,
\(\ret{\mach_c}\ \mach_r\) holds.
